\Large \bf A first look at auditing in a blockchain world

### 2018-09-26 auditing/Latex/sections/01-intro.tex

\paragraph{\textbf{Relevance.}} Our work can be viewed as a case study of cryptographers working with an outside profession to address a real-world problem. The result is not a new protocol but a two-way knowledge transfer between professions. While displacing auditors is occasionally a target of cryptographers~\cite{dagher2015provisions,narula2018zkledger}, auditing itself is also occasionally studied directly at venues like Financial Cryptography~\cite{Swi97,BFS98,grigg2000financial}.

@@

%------------------------------------------------------------------------------------------------
\subsection{Cryptoassets and firms that hold them}
The central component of a financial report is the firm's balance sheet which lists assets and liabilities. We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items contingent on blockchain technologies. Cryptoassets include cryptocurrencies and other tokens of tradeable value. Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution (\eg bitcoin and ether). For blockchains that allow developers to deploy custom decentralized applications, the applications might issue and manage the ownership of custom tokens. In the case of ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.

>>>>

\paragraph{\textbf{Relevance.}} Our work can be viewed as a case study of cryptographers working with an outside profession to address a real-world problem. The result is not a new protocol but a two-way knowledge transfer between professions. While displacing auditors is occasionally a target of cryptographers~\cite{dagher2015provisions,narula2018zkledger}, auditing itself is also occasionally studied directly~\cite{grigg2000financial} or indirectly~\cite{Swi97,BFS98} at venues like Financial Cryptography.

@@

%------------------------------------------------------------------------------------------------
\subsection{Cryptoassets and firms that hold them}
The central component of a financial report is the firm's balance sheet which lists assets and liabilities. We use the term \textit{cryptoasset} and \textit{cryptoliability} to refer to items contingent on blockchain technologies. Cryptoassets include cryptocurrencies and other tokens of tradeable value. Without loss of generality, we assume cryptocurrencies are native to their underlying blockchain, can be transacted directly, and are used to pay fees for transaction execution (\eg bitcoin and ether). For blockchains that allow developers to deploy custom decentralized applications, the applications might issue and manage the ownership of custom tokens. In the case of Ethereum, these tokens are often \textit{ERC20} tokens~\cite{erc20}, where \textit{ERC20} is sometimes misunderstood to mean what the token represents; rather, \textit{ERC20} is a technical standard about how token transactions are invoked.
